Active Learning for SAT Solver Benchmarking

### 2024-04-22 paper_jar/paper.tex
Refer to conference version in Intro

\title[Active Learning for SAT Solver Benchmarking]{Active Learning for SAT Solver Benchmarking} % short and long title
%JB: not sure if we should use a new title or not; in past special issues of journal, both options (re-use conference-version title or choose new title) were used

@@

\section{Introduction}
\label{sec:intro}

% TODO: somewhere in introduction, refer to conference version ("fuchs2023active") and state what has changed in journal version
% TODO: if appropriate, extend with motivation/results regarding runtime discretization and prediction models

@@

We evaluate our approach with the SAT Competition~2022 Anniversary Track dataset~\cite{sat2022}, consisting of 5355~instances and runtimes of 28~solvers.
We perform cross-validation by treating each solver once as the new solver and learning to predict the PAR-2 rank of that solver.
On average, our predictions reach about \SI{92}{\%} accuracy with only about \SI{10}{\%} of the runtime required to evaluate these solvers on the complete set of instances.

Our entire source code\footnote{\url{https://github.com/mathefuchs/al-for-sat-solver-benchmarking}} and experimental data\footnote{\url{https://github.com/mathefuchs/al-for-sat-solver-benchmarking-data}} are available on GitHub.

@@

\subsection{Runtime Discretization and Prediction}

@@

\subsection{Instance Frequency in Selected Benchmarks}
% TODO tf: Frequency of instances
\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{../plots/instoccs.pdf}
  \caption{Frequency of how often individual problem instances are selected within all active-learning benchmarks. Instances that are choosen more frequently are intuitively more important to distinguish solver runtimes.}
\end{figure}

>>>>

\title[Active Learning for SAT Solver Benchmarking]{Active Learning for SAT Solver Benchmarking} % short and long title

@@

\section{Introduction}
\label{sec:intro}
% TODO: if appropriate, extend with motivation/results regarding runtime discretization and prediction models

@@

We evaluate our approach with the SAT Competition~2022 Anniversary Track dataset~\cite{sat2022}, consisting of 5355~instances and runtimes of 28~solvers.
We perform cross-validation by treating each solver once as the new solver and learning to predict the PAR-2 rank of that solver.
On average, our predictions reach about \SI{92}{\%} accuracy with only about \SI{10}{\%} of the runtime required to evaluate these solvers on the complete set of instances.
Our entire source code\footnote{\url{https://github.com/mathefuchs/al-for-sat-solver-benchmarking}} and experimental data\footnote{\url{https://github.com/mathefuchs/al-for-sat-solver-benchmarking-data}} are available on GitHub.

This article is an extended version of a conference paper with the same name~\cite{fuchs2023active}.
% TODO: not sure if we should choose a new title or not; in past special issues of journal, both options (re-use conference-version title or choose new title) were used
In particular, we significantly extended the analysis of runtime-prediction approaches (cf.~Section~\ref{sec:exdesign:disc-pred}) and added an evaluation of how often problem instances were selected in benchmarks (cf.~Section~\ref{sec:eval:inst-freq}).
% TODO: before submission, we should check which other changes we made and list them here accordingly

@@

\subsection{Runtime Discretization and Prediction}
\label{sec:exdesign:disc-pred}

@@

\subsection{Instance Frequency in Selected Benchmarks}
\label{sec:eval:inst-freq}

% TODO tf: Frequency of instances
\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{../plots/instoccs.pdf}
  \caption{Frequency of how often individual problem instances are selected within all active-learning benchmarks. Instances that are choosen more frequently are intuitively more important to distinguish solver runtimes.}
\end{figure}
